untitled

### 2016-05-10 linear.tex
sample results

\begin{align}
  \ii\sigma W &= \ii k \dd v_r + \dd v_z^\prime +
  \dd v_r \p_r\ln{\rho} + \dd v_z\p_z\ln{\rho},\label{lin_mass}\\
  -\ii\sigma\dd v_r  &= 2\Omega\dd v_\phi + 
  \delta\bm{F}\cdot\hat{\bm{r}},\label{lin_xmom}\\
  \ii\sigma\dd v_\phi &= \frac{\kappa^2}{2\Omega}\dd v_r + \frac{\p
    v_\phi}{\p z}\dd v_z, \label{lin_ymom}\\
  -\ii\sigma\dd v_z &=  \delta\bm{F}\cdot\hat{\bm{z}},\label{lin_zmom}\\
  \ii\sigma Q &= \frac{P}{\rho}\left(\ii k \dd v_r + \dd
               v_z^\prime\right) + \frac{1}{\rho}\left(\dd v_r\p_rP + \dd v_z \p_zP\right)\notag\\
                &\phantom{=}-\frac{P}{\rho} \dd v_r\p_r \ln{c_s^2} - \frac{\dd\mathcal{C}}{\rho},\label{lin_energy}
\end{align}  
where $^\prime \equiv \p_z$; $\dd\bm{F}$ is the linearized pressure force, given in Appendix
\ref{lin_press}; and 
%\begin{align}
%  \delta \bm{F} \equiv \frac{\dd\rho}{\rho^2}\nabla P -
%  \frac{1}{\rho}\nabla\dd P, 
%\end{align}
$\dd\mathcal{C}$ is the linearized dust-duffusion function, given in
Appendix \ref{lin_dust}.  We consider stopping times appropriate for
small grains in the Epstein regime. Note that for the axisymmetric
problem, $\dd\bm{F}$ is purely meridional.

@@

This means that for the perfectly coupled problem, we have a pair of
ODEs for $Q$ and $\dd v_z$, and two boundary conditions are needed. 
This is expected since this problem is exactly 
equivalent to that in adiabatic hydrodynamics \citep[e.g.]{lubow93}. When
$\tstop\neq0$, we require three boundary conditions. {\bf WHAT?? Why odd
  number of BCs? Shouldn't we have even number of BCs? We have
two boundaries? I've only seen problems like this involving even
number of BCs.} In this case we impose $\dd v_z =0$ at $z=\pm
z_\mathrm{max}$, and consider even modes about the midplane such that
$\dd v_z^\prime(0) = 0$.

>>>>

\begin{align}
  \ii\sigma W &= \ii k \dd v_r + \dd v_z^\prime +
  \dd v_r \p_r\ln{\rho} + \dd v_z\p_z\ln{\rho},\label{lin_mass}\\
  -\ii\sigma\dd v_r  &= 2\Omega\dd v_\phi + 
  \delta\bm{F}\cdot\hat{\bm{r}},\label{lin_xmom}\\
  \ii\sigma\dd v_\phi &= \frac{\kappa^2}{2\Omega}\dd v_r + \frac{\p
    v_\phi}{\p z}\dd v_z, \label{lin_ymom}\\
  -\ii\sigma\dd v_z &=  \delta\bm{F}\cdot\hat{\bm{z}},\label{lin_zmom}\\
  \ii\sigma Q &= \frac{P}{\rho}\left(\ii k \dd v_r + \dd
               v_z^\prime\right) + \frac{1}{\rho}\left(\dd v_r\p_rP + \dd v_z \p_zP\right)\notag\\
                &\phantom{=}-\frac{P}{\rho}\left( \dd v_r\p_r
               \ln{c_s^2} + \dd v_z \p_z\ln{c_s^2}\right)-
               \frac{\dd\mathcal{C}}{\rho},\label{lin_energy} 
\end{align}  
where $^\prime \equiv \p_z$; $\dd\bm{F}$ is the linearized pressure force, given in Appendix
\ref{lin_press}; and 
%\begin{align}
%  \delta \bm{F} \equiv \frac{\dd\rho}{\rho^2}\nabla P -
%  \frac{1}{\rho}\nabla\dd P, 
%\end{align}
$\dd\mathcal{C}$ is the linearized dust-duffusion function, given in
Appendix \ref{lin_dust}. We consider stopping times appropriate for
small grains in the Epstein regime. Note that for the axisymmetric
problem, $\dd\bm{F}$ is purely meridional.

@@

This means that for the perfectly coupled problem, we have a pair of
ODEs for $Q$ and $\dd v_z$, and two boundary conditions are needed. 
This is expected since this problem is exactly 
equivalent to that in adiabatic hydrodynamics \citep[e.g.]{lubow93}. When
$\tstop\neq0$, we require three boundary conditions. {\bf WHAT?? Why odd
  number of BCs? Shouldn't we have even number of BCs? We have
two boundaries? I've only seen problems like this involving even
number of BCs.} In this case we impose $\dd v_z =0$ at $z=\pm
z_\mathrm{max}$, and classify modes according to their symmetry about
the midplane: `even' modes with $\dd v_z^\prime(0) = 0$, and `odd' 
modes with $\dd v_z(0)=0$.

### 2016-05-10 result.tex
sample results

\begin{figure}
\includegraphics[width=\linewidth]{figures/eigenvalues}
\caption{do not believe}
\end{figure}

>>>>

We consider a globally isothermal disk, $c_s=\mathrm{const.}$, by
setting $q=0$ in the equation of state, Eq. \ref{eos}, and a flat mid-plane 
gas density, $\rhog(0) = \mathrm{const.}$, so there is no global
radial pressure gradient at the disk midplane. The stopping time is
prescribed as 
\begin{align}
  \tstop = t_\mathrm{s0}\frac{\rho(z=0)}{\rho(z)}. 
\end{align}

As an example, we set the dust-to-gas ratio $\tepsilon_0=0.025$, dust 
scale height $H_\mathrm{d}=0.4\Hgas$, and stopping time
$t_\mathrm{s0}=0.02$. We consider modes with radial wavenumber
$k_x\Hdust=2\pi$. The vertical domain size is set to 
$\zmax=2\Hgas$ and we use $N=513$ grid points. Fig. \ref{eigen_map}
shows a map of the eigenvalues in the $(\omega, s)$ plane.

\begin{figure}
  \includegraphics[width=\linewidth]{figures/eigenvalues}
  \caption{Eigenvalues found for the fiducial isothermal dusty
    problem.
  \label{eigen_map}} 
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/eigenvec}
  \caption{Example eigenvectors from the fiducial case. 
  \label{eigen_vec}} 
\end{figure}
